---
title: "CRI Replication Initiative"
output: html_document
---

```{r setup, include=FALSE}
stopifnot(require(dplyr))
stopifnot(require(ggplot2))
stopifnot(require(readr))
stopifnot(require(reshape2))
stopifnot(require(forcats))
stopifnot(require(readxl))
```


```{r}
cri_2006 <- read_csv('../raw/ZA4700.csv')
#list rows of data that have missing values

```

According to the codebook https://dbk.gesis.org/dbksearch/file.asp?file=ZA4700_bq.pdf 
The six different welfare attitudes are
Jobs (V25)
Unemployment (V30)
Income (V31)
Retirement (V28)
Housing (V33)
Healthcare(V27)

After doing listwise deletion, the observations decrease from 48,641 to 42,809. 
```{r}
positions <- c('V1', 'V2', 'V3a','V25', 'V30', 'V31', 'V28', 'V33', 'V27')
df <- cri_2006 %>% 
    select(positions) %>% 
    rename(jobs='V25') %>% 
    rename(unemployment='V30') %>% 
    rename(income='V31') %>% 
    rename(retirement='V28') %>% 
    rename(housing='V33') %>% 
    rename(healthcare='V27') %>% 
    rename(studyno='V1') %>% 
    rename(country='V3a') %>% 
    rename(respondentid='V2') %>% 
    na.omit()

nrow(df)
```

Recode to binary. So `probably not` and `definitely no`t are a `0` and `probably should be` and `definitely should` are a `0`. Excuse the repetitive code for now
```{r}
unique(df$jobs)
fct_count(df$jobs)
coltobinary <- c('jobs', 'unemployment', 'income', 'retirement', 'housing', 'healthcare')


df$jobs <- fct_collapse(df$jobs,
                         "0" = c("Definitely should not be", "Probably should not be"),
                         "1" = c("Definitely should be", "Probably should be"))
df$unemployment <- fct_collapse(df$unemployment,
                         "0" = c("Definitely should not be", "Probably should not be"),
                         "1" = c("Definitely should be", "Probably should be"))
df$income <- fct_collapse(df$income,
                         "0" = c("Definitely should not be", "Probably should not be"),
                         "1" = c("Definitely should be", "Probably should be"))
df$retirement <- fct_collapse(df$retirement,
                         "0" = c("Definitely should not be", "Probably should not be"),
                         "1" = c("Definitely should be", "Probably should be"))
df$housing <- fct_collapse(df$housing,
                         "0" = c("Definitely should not be", "Probably should not be"),
                         "1" = c("Definitely should be", "Probably should be"))
df$healthcare <- fct_collapse(df$healthcare,
                         "0" = c("Definitely should not be", "Probably should not be"),
                         "1" = c("Definitely should be", "Probably should be"))


```

The country level independent variables are foreign-born(foreignpct), social welfare expenditures (socx), employment rate(emprate), net migration(netmig).
The specific countries we would want are Australia, Canada, France, Germany, Ireland, Japan, New Zealand, Norway, Spain, Sweden, Switzerland, the United Kingdom, and the United States.
```{r}
indv <- read_csv('../raw/bradyfinnigan2014countrydata.csv')

#only select independent variables of interest and country code
#filter out to my year of data = 2006
findv <- indv %>% 
    select(1:7, "country") %>% 
    filter(year==2006)
```
The country codes were specific to this file and not an internationally recognized standard so these had to be manually set in order to join with the other independent variables.
```{r}
unique(df$country)
df$country <- df$country %>% 
    recode('AU-Australia' = 'Australia') %>% 
    recode('CA-Canada' = 'Canada') %>% 
    recode('FR-France' = 'France') %>% 
    recode('DE-Germany' = 'Germany') %>% 
    recode('IE-Irelan' = 'Ireland') %>% 
    recode('JP-Japan' = 'Japan') %>% 
    recode('NZ-New Zealand' = 'New Zealand') %>% 
    recode('NO-Norway'= 'Norway') %>% 
    recode('ES-Spain'= 'Spain') %>% 
    recode('SE-Sweden' = 'Sweden') %>% 
    recode('CH-Switzerland' = 'Switzerland') %>% 
    recode('US-United States' = "United States") %>% 
    trimws()
table(df$country)

```

Only keep the countries we care about
```{r}
cwc <-  c('Australia', 'Canada', 'France','Germany', 'Ireland', 'Japan', 'New Zealand', 'Norway', 'Spain', 'Sweden', 'Switzerland', 'United States')
df <- df[df$country %in% cwc,]
nrow(df)
```
Join original dataframe to other independent variable table
```{r}
finaldf <- inner_join(df, findv, by="country")
write_csv(finaldf, "../processed/cri_df_2006.csv")
```

