---
title: "CRI Replication Initiative"
output: html_document
---

```{r setup, include=FALSE}
stopifnot(require(dplyr))
stopifnot(require(ggplot2))
stopifnot(require(readr))
stopifnot(require(reshape2))
stopifnot(require(forcats))
stopifnot(require(readxl))
```
Initially when I ran the below code, I attempted to do listwise deletion of the entire 
dataset, but that returned 0 rows since all rows had at least one N/A value. This leads
me to believe that the listwise deletion will have to occur later on.

```{r}
cri_1996 <- read_csv('~/Downloads/ZA2900.csv')
#list rows of data that have missing values
cri_1996[!complete.cases(cri_1996),]
ndata <- na.omit(cri_1996)
View(ndata)
         
```

According to the codebook file:///Users/208456/Downloads/ZA2900_cdb.pdf
The six different welfare attitudes are
Jobs (V36)
Unemployment (V41)
Income (V42)
Retirement (V39)
Housing (V44)
Healthcare(V38)

After doing listwise deletion, the observations decrease from 35,313 to 30,287. 
```{r}
positions <- c('v1', 'v2', 'v3','v36', 'v41', 'v42', 'v39', 'v44', 'v38')
df <- cri_1996 %>% 
    select(positions) %>% 
    rename(jobs='v36') %>% 
    rename(unemployment='v41') %>% 
    rename(income='v42') %>% 
    rename(retirement='v39') %>% 
    rename(housing='v44') %>% 
    rename(healthcare='v38') %>% 
    rename(studyno='v1') %>% 
    rename(country='v3') %>% 
    rename(respondentid='v2') %>% 
    na.omit()

```

Recode to binary. So `probably not` and `definitely no`t are a `0` and `probably should` and `definitely should` are a `0`. Excuse the repetitive code for now
```{r}
fct_count(df$jobs)
coltobinary <- c('jobs', 'unemployment', 'income', 'retirement', 'housing', 'healthcare')


df$jobs <- fct_collapse(df$jobs,
                         "0" = c("Definitely not", "Probably not"),
                         "1" = c("Definitely should", "Probably should"))
df$unemployment <- fct_collapse(df$unemployment,
                         "0" = c("Definitely not", "Probably not"),
                         "1" = c("Definitely should", "Probably should"))
df$income <- fct_collapse(df$income,
                         "0" = c("Definitely not", "Probably not"),
                         "1" = c("Definitely should", "Probably should"))
df$retirement <- fct_collapse(df$retirement,
                         "0" = c("Definitely not", "Probably not"),
                         "1" = c("Definitely should", "Probably should"))
df$housing <- fct_collapse(df$housing,
                         "0" = c("Definitely not", "Probably not"),
                         "1" = c("Definitely should", "Probably should"))
df$healthcare <- fct_collapse(df$healthcare,
                         "0" = c("Definitely not", "Probably not"),
                         "1" = c("Definitely should", "Probably should"))
View(df)



```

The country level independent variables are foreign-born(foreignpct), social welfare expenditures (socx), employment rate(emprate), net migration(netmig).
The specific countries we would want are Australia, Canada, France, Germany, Ireland, Japan, New Zealand, Norway, Spain, Sweden, Switzerland, the United Kingdom, and the United States.
```{r}
indv <- read_excel('~/Downloads/bradyfinnigan2014countrydata.xls')
View(indv)

#only select independent variables of interest and country code
#filter out to my year of data = 1996
findv <- indv %>% 
    select(1:7, "country") %>% 
    filter(year==1996)
```
The country codes were specific to this codebook (file:///Users/208456/Downloads/ZA2900_cdb.pdf) and not an internationally recognized standard so these had to be manually set in order to join with the other independent variables.
```{r}

df$country <- df$country %>% 
    recode('aus' = 'Australia') %>% 
    recode('cdn' = 'Canada') %>% 
    recode('f' = 'France') %>% 
    fct_collapse('Germany' = c('D-E', 'D-W')) %>% 
    recode('irl' = 'Ireland') %>% 
    recode('j' = 'Japan') %>% 
    recode('nz' = 'New Zealand') %>% 
    recode('n'= 'Norway') %>% 
    recode('e'= 'Spain') %>% 
    recode('s' = 'Sweden') %>% 
    recode('ch' = 'Switzerland') %>% 
    recode('usa' = "United States") %>% 
    trimws()
table(df$country)

```

Only keep the countries we care about
```{r}
cwc <-  c('Australia', 'Canada', 'France','Germany', 'Ireland', 'Japan', 'New Zealand', 'Norway', 'Spain', 'Sweden', 'Switzerland', 'United States')
df <- df[df$country %in% cwc,]

```
Join original dataframe to other independent variable table
```{r}
finaldf <- inner_join(df, findv, by="country")
write_csv(finaldf, "~/Desktop/cri_df_1996.csv")
```

